\chapter{E-5 Combining different modes of transport}

A load of 20 tonnes needs to be transported on a rouate passing through five cities,
with a choice of three different modes of transport: rail, road, and air. In any
of the three intermediate cities it is possible to change the mode of transport
but the load uses a single mode of transport between two consecutive cities.
Refer to \cref{table:transport-costs} for the cost of the various modes of
transport between pairs of cities.

Furthermore, changing the mode of tranport incurs an associated cost. This cost
is indepdependent of location. Refer to \cref{table:transfer-costs} for these
costs.

How should we organize the transport of the load at the least cost?

\section{Parameters}

\begin{syms}

\item[$M$] enumerates the $n=3$ modes of transport:
    $\left\lbrace \texttt{rail}, \texttt{road}, \texttt{air}\right\rbrace$,
    with $M=\left\lbrace 1, \ldots, n\right\rbrace$

\item[$L$] enumerates the $k=5$ legs of the route between the cities, ie.
    $L=\left\lbrace 1,\ldots, k\right\rbrace$

\item[$c_{ml}$] denotes the transportation cost per tonne on leg $l\in L$ of the route
    using mode $m\in M$

\item[$t_{ij}$] denotes the cost per tonne of transfering the cargo from mode $i\in M$ to mode
    $j\in M$ at a given city

\item[$q$] denotes the weight of the cargo in tonnes with $q=20$ tonnes

\end{syms}

Refer to \cref{table:transport-costs} for values of $c_{ml}$ and to \cref{table:transfer-costs}
for values of $t_{ij}$.

\begin{table}[h]
    \center
    \caption{Transportation costs between pairs of cities using various modes of transport}
    \label{table:transport-costs}
    \begin{tabu}{lcccc}
        \hline
        \rowfont[lcccc]{\bfseries} & 1-2 & 2-3 & 3-4 & 4-5 \\
        \hline
        \textbf{Rail} & 30 & 25 & 40 & 60 \\
        \textbf{Road} & 25 & 40 & 45 & 50 \\
        \textbf{Air} & 40 & 20 & 50 & 45 \\
        \hline
    \end{tabu}
\end{table}

\begin{table}[h]
    \center
    \caption{Costs of changing mode of transport}\label{table:transfer-costs}
    \begin{tabu}{lccc}
        \hline
        \rowfont[lccc]{\bfseries} from/to & Rail & Road & Air \\
        \hline
        \textbf{Rail} & 0 & 5 & 12 \\
        \textbf{Road} & 8 & 0 & 10 \\
        \textbf{Air} & 15 & 10 & 0 \\
        \hline
    \end{tabu}
\end{table}

\section{Decision variables}

\begin{syms}

\item[$x_{ml}$] indicates that mode $m\in M$ is used on leg $l\in L$ of the route;
    $x_{ml} \in \left\lbrace 0, 1\right\rbrace$; for convenience, let
    $\vect{x} \in \left\lbrace 0, 1\right\rbrace^{n\times k}$ with entries
    $x_{ml}$

\item[$y_{ijl}$] indicates whether cargo is transfered from mode $i\in M$ to mode
    $j\in M$ after leg $l\in L$ of the journey; $y_{ijl}\in\left\lbrace 0, 1\right\rbrace$;
    for convenience, we define the tensor 
    $\vect{y} \in\left\lbrace 0, 1\right\rbrace^{n\times n\times k}$

\end{syms}

\section{Model}

The total tranportation cost is given by

\begin{equation}
    g(\vect{x}) = \sum_{m\in M}\sum_{l\in l} c_{ml} x_{ml}.
\end{equation}

The total cost of transfering the cargo between modes of transportation
is

\begin{equation}
    h(\vect{y}) = \sum_{i\in M}\sum_{j\in M}\sum_{l\in L\setminus \left\lbrace k\right\rbrace}
    t_{ij}y_{ijl}
\end{equation}

\begin{mini!}
    {\vect{x}}{f(\vect{x},\vect{y})=g(\vect{x}) +h(\vect{y}) \protect\label{eq:e5-obj}}{\label{eq:e5}}{}
    \addConstraint{\sum_{m\in M}x_{ml}}{& = 1, \forall l\in L \protect\label{eq:e5-ctr1}}
    \addConstraint{\sum_{i, j\in M} y_{ijl}}{& = 1, \forall l\in L\setminus\left\lbrace k\right\rbrace \protect\label{eq:e5-ctr2}}
    \addConstraint{x_{il}}{& \geq y_{ijl}, \forall i, j \in M, l\in L\setminus\left\lbrace k\right\rbrace \protect\label{eq:e5-ctr3}}
    \addConstraint{x_{ml}}{& \in \left\lbrace 0, 1\right\rbrace, \forall m\in M, l\in L \protect\label{eq:e5-ctr4}}
    \addConstraint{y_{ijl}}{& \in \left\lbrace 0, 1\right\rbrace, \forall i,j \in M, l\in L \protect\label{eq:e5-ctr5}}
\end{mini!}

\section{Results}
