\chapter{F-4 Airline hub location}

The airline FAL (French Air Lines) sepcializes in freight transport. The company
links the major French cities with cities in the United States,
nameley Atlanta, Boston, Chicago, Marseille, Nice, and Paris. The average
quantities in tonnes transported every day by this company between these cities
are given in \cref{table:f4-quant}.

We shall assume that the transport cost between two cities $i$ and $j$
is proportional to the distance that seperates them. The distances in miles
are given in \cref{table:f4-dist}.

The airline is planning to use two cities as connection paltforms
(\textbf{hubs}) to reduce the transport costs. Every city is then assigned a single
hub. The traffic between cities assigned to a given hub $H_1$ to the cities
assigned to the other hub $H_2$ is all routed through the single connection
form $H_1$ to $H_2$ which allows the airline to reduce the transport cost
by 20\%. Determine the two cities to be chosen as hubs in order to minimize
the transport cost.

\section{Parameters}

\begin{syms}

\item[$C$] enumerates $m=5$ cities: 
$\left\lbrace \texttt{Atlanta}, \texttt{Boston}, \texttt{Chicago}, \texttt{Marseille}, \texttt{Nice}\right\rbrace$,
ie. $C=\left\lbrace 1, \ldots, n\right\rbrace$

\item[$n$] denotes the number of hubs to choose, with $n=2$
    
\item[$q_{ij}$] denotes the average quantity of goods in tonnes transported between city
    $i\in C$ and $j\in C$ in a given day

\item[$d_{ij}$] denotes the distance from city $i\in C$ to city $j\in C$

%\item[$f_{ij}$] is the non-reduced transportation cost from city $i\in C$ to city $j\in C$

\item[$c_{ijkl}$] is proportional to the transportation cost from city $i\in C$ to city $j\in C$ through
    hubs $k\in C$ and $l\in C$

\item[$r$] is the reduced hub to hub transport cost factor, with $r=0.8$

\end{syms}

$c_{ijkl}$ is calculated from $d_{ij}$ and $r$ as follows:

\begin{equation}
    c_{ijkl} = d_{ik} + rd_{kl} + d_{lj}, \forall i,j,k,l \in C
\end{equation}

\emph{Note:} When any one of the two suscripts are equal, we have $d_{ii}=0$.

\begin{table}
    \center
    \caption{Average daily quantities of freight in tonnes}\label{table:f4-quant}
    \begin{tabu}{lcccccc}
        \hline
        \rowfont[lcccccc]{\bfseries} & Atlanta & Boston & Chicago & Marseille & Nice & Paris \\
        \hline
        \textbf{Atlanta} & 0 & 500 & 1000 & 300 & 400 & 1500 \\
        \textbf{Boston} & 1500 & 0 & 250 & 630 & 360 & 1140 \\
        \textbf{Chicago} & 400 & 510 & 0 & 460 & 320 & 490 \\
        \textbf{Marseille} & 300 & 600 & 810 & 0 & 820 & 310 \\
        \textbf{Nice} & 400 & 100 & 420 & 730 & 0 & 970 \\
        \textbf{Paris} & 350 & 1020 & 260 & 580 & 380 & 0 \\
        \hline
    \end{tabu}
\end{table}

\begin{table}
    \center
    \caption{Distances between pairs of cities in miles}\label{table:f4-dist}
    \begin{tabu}{lccccc}
        \hline
        \rowfont[lccccc]{\bfseries} & Boston & Chicago & Marseille & Nice & Paris \\
        \hline
        \textbf{Atlanta} & 945 & 605 & 4667 & 4749 & 4394 \\
        \textbf{Boston} & & 866 & 3726 & 3806 & 3448 \\
        \textbf{Chicago} & & & 4471 & 4541 & 4152 \\
        \textbf{Marseille} & & & & 109 & 415 \\
        \textbf{Nice} & & & & & 431 \\
        \hline
    \end{tabu}
\end{table}

\newpage

\section{Decision variables}

\begin{syms}

\item[$x_{ijkl}$] indicates that the cargo flows from city $i\in C$ to city
    $j\in C$ via hubs $k\in C$ and $l\in C$, in other words

    $x_{ijkl} = \begin{cases}1 & \text{cargo flows from city }i\text{ to }j\text{ via hub }k\text{ to }l \\
        0 & \text{otherwise}
    \end{cases}$,

    for convenience, define the tensor $\vect{x} \in \left\lbrace 0, 1\right\rbrace^{n\times n\times n\times n}$
    with entries $x_{ijkl}$

\item[$y_i$] indicates whether city $i\in C$ is a hub, in other words

        $y_i = \begin{cases}1 & \text{city }i\text{ is a hub} \\
            0 & \text{otherwise}
        \end{cases}$,

    for convenience, define the tuple $\vect{y} = \left( y_1,\ldots, y_n\right) \in \left\lbrace 0, 1\right\rbrace^n$


\end{syms}

\section{Model}

\begin{mini!}
    {\vect{x}}{f(\vect{x})=\mathop{\sum\sum\sum\sum}_{i,j,k,l\in C} c_{ijkl} c_{ijkl}q_{ij}x_{ijkl} \protect\label{eq:f4-obj}}{\label{eq:f4}}{}
    \addConstraint{\sum_{i\in C} y_i}{= n \protect\label{eq:f4-ctr1}}
    \addConstraint{\mathop{\sum\sum}_{k,l\in C} x_{ijkl}}{= 1, \forall i, j\in C \protect\label{eq:f4-ctr-2}}
    \addConstraint{x_{ijkl}}{\leq y_{k}, \forall i,j, k, l \in C \protect\label{eq:f4-ctr-3}}
    \addConstraint{x_{ijkl}}{\leq y_{l}, \forall i,j, k, l \in C \protect\label{eq:f4-ctr-4}}
    \addConstraint{x_{ijkl}}{\in \left\lbrace 0, 1\right\rbrace, \forall i,j,k,l \in C \protect\label{eq:f4-ctr-5}}
    \addConstraint{y_i}{\in \left\lbrace 0, 1\right\rbrace, \forall i\in C \protect\label{eq:f4-ctr-6}}
\end{mini!}
\section{Results}
