\chapter{E-1 Car rental}

A small car rental company has a fleet of 94 vechiles distributed among its
10 agencies. The location of every agency is given by its geographical coordinates
$X$ and $Y$ in a grid based on kilometers. We assume that the road distance
between agencies is approximately 1.3 times the Euclidean distance. Refer to
\cref{table:coords} for the geographical coordinates of all agencies, the inventory
of cars required the next morning, and the inventory of cars in the evening
preceeding this day. Refer to \cref{table:car-stock} for the available and required
inventories of the various agencies.

Suppose the cost for transporting a car is $\euro{}0.50$ per km, determine the
movements of cars that allow the company to re-establish the required numbers of
cars at all agencies, minimizing the total cost incurred for transport.

\section{Parameters}

\begin{syms}

\item[$A$] enumerates $n=10$ rental agencies, ie. $A=\left\lbrace 1,\ldots, n\right\rbrace$

\item[$\vect{X}_a$] denotes the geographical coordinates of an agency $a\in A$, with
    $\vect{X}_a \in \Real^2$, for convience let $\vect{X} \in \Real^{2\times n}$ with
    columns $\vect{X}_a, \forall a\in A$

\item[$r_a$] number of cars required by agency $a\in A$ on next morning

\item[$s_a$] number of cars agency $a\in A$ has in the evening

\item[$E$] part of the partition of $A$ with 
    $E= \left\lbrace a\in A : s_a > r_a \right\rbrace \subset A$

\item[$N$] part of the parition of $A$ with
    $N = \left\lbrace a\in A: s_a < r_a \right\rbrace \subset A$

\item[$c$] transporation cost in \euro{} / km, with $c=\euro{}0.50$ / km

\item[$\lambda$] Euclidean distance to road distance multiplier, with $\lambda=1.3$

\end{syms}

\begin{table}[h]
    \center
    \caption{Geographical coordinates of agencies}\label{table:coords}
    \begin{tabu}{lcccccccccc}
        \hline
        \rowfont[lcccccccccc]{\bfseries} Agency $a$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10\\
        \hline
        \textbf{X coordinate (km grid)} $X_a^{(x)}$ & 0 & 20 & 18 & 30 & 35 & 33 & 5 & 5 & 11 & 2 \\
        \textbf{Y coordinate (km grid)} $X_a^{(y)}$ & 0 & 20 & 10 & 12 & 0 & 25 & 27 & 10 & 0 & 15 \\
        \hline
    \end{tabu}
\end{table}

\begin{table}[h]
    \center
    \caption{Available and required inventory of agencies}\label{table:car-stock}
    \begin{tabu}{lcccccccccc}
        \hline
        \rowfont[lcccccccccc]{\bfseries} Agency $a$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10\\
        \hline
        \textbf{Cars present} $s_a$ & 8 & 13 & 4 & 8 & 12 & 2 & 14 & 11 & 15 & 7 \\
        \textbf{Cars required} $r_a$ & 10 & 6 & 8 & 11 & 9 & 7 & 15 & 7 & 9 & 12 \\
        \hline
    \end{tabu}
\end{table}

\section{Decision variable}

\begin{syms}

    \item[$x_{ij}$] denotes the number of cars transpored from an agency
        with excess $i\in E$ to an agency with shortage $j\in N$;
        $0 \leq x_{ij} \in \Int$; for convience let $\vect{x} \in \Int^{|E|\times|N|}$
        with entries $x_{ij}$

\end{syms}

\section{Model}

\begin{mini!}
    {\vect{x}}{f(\vect{x})=\sum_{i\in E}\sum_{j\in N} c \lambda x_{ij} \sqrt{\vect{X}_i - \vect{X}_j} \protect\label{eq:e1-obj}}{\label{eq:e1}}{}
    \addConstraint{\sum_{i\in E} x_{ij}}{& = s_j - r_j, \forall j\in N \protect\label{eq:e1-ctr1}}
    \addConstraint{\sum_{j\in N} x_{ij}}{& = s_i - r_i, \forall i\in N \protect\label{eq:e1-ctr2}}
    \addConstraint{x_{ij}}{& \geq 0, \forall (i,j) \in E\times N \protect\label{eq:e1-ctr3}}
\end{mini!}


\section{Results}
